High-Fidelity Counterfactual Explanations through Conformal Prediction

### 2023-04-24 notebooks/mnist.qmd
more work on paper

### ECCo

@@

```{julia}
# Data:
counterfactual_data.X = pre_process.(counterfactual_data.X)
X, y = CounterfactualExplanations.DataPreprocessing.unpack_data(counterfactual_data)
X = table(permutedims(X))
labels = counterfactual_data.output_encoder.labels
input_dim, n_obs = size(counterfactual_data.X)
n_digits = Int(sqrt(input_dim))
output_dim = length(unique(labels))
```

>>>>

### ECCCo

@@

```{julia}
# Data:
n_obs = 1000
counterfactual_data = load_mnist(n_obs)
counterfactual_data.X = pre_process.(counterfactual_data.X)
X, y = CounterfactualExplanations.DataPreprocessing.unpack_data(counterfactual_data)
X = table(permutedims(X))
labels = counterfactual_data.output_encoder.labels
input_dim, n_obs = size(counterfactual_data.X)
n_digits = Int(sqrt(input_dim))
output_dim = length(unique(labels))
```
